Accounting for Fiber Collisions in the Galaxy Power Spectrum Measurements

### 2015-12-31 fc_paper/fc_paper.tex

As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe, because the fiber collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales. SDSS-III BOSS, in particular, has an angular fiber collision scale of $62\arcsec$. This corresponds to $\sim 0.43 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}). While this may seem like a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and need be accounted for in order to probe smaller scales and higher order statistics such as the three-point correlation function or the bispectrum. Future spectroscopic surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}), will use robotic fiber positioner technology. Unfortunately this will only increase the effect of fiber collisions. Therefore, accounting for fiber collisions will be an unavoidable challenge for clustering statistics in the near future.

>>>>

As our cosmological surveys extend further to higher redshifts, the systematic effect becomes more severe, because the fiber collision angular scale corresponds to a larger comoving scale, thereby affecting our measurements on larger scales. SDSS-III BOSS, in particular, has an angular fiber collision scale of $62\arcsec$. This corresponds to $\sim 0.43 \;\mathrm{Mpc}/h$ at the center of the survey's redshift redshift range; fiber-collided galaxies account for $\sim 5\%$ of the galaxy sample (\citealt{Anderson:2012aa}). While this may seem like a relatively small fraction of redshifts, its effect on clustering measurements such as the power spectrum is significant and need be accounted for in order to probe smaller scales and higher order statistics such as the three-point correlation function or the bispectrum. Future spectroscopic surveys such as the Dark Energy Survey Instrument (DESI; \citealt{Schlegel:2011aa, Morales:2012aa, Makarem:2014aa}), will use robotic fiber positioner technology. Unfortunately this will not resolve the issues caused by fiber collisions and the effects of collisions caused by the fiber positions will need to be understood. Therefore, accounting for fiber collisions remains an unavoidable challenge for clustering statistics in the near future.
